6.867 Problem Set 1

### 2015-12-10 Project/Latex/Paper.tex
[project] update that table.

@@

\begin{center}
\begin{tabular}{lr}
\toprule
Feature  &  Weight\\
\midrule
intercept & 9.114\\
log(Word Count) & 0.736\\
Desk: Foreign & 0.561\\
Desk: Travel & -0.478\\
Section: World & -0.410\\
Type: BlogPost & -0.394\\
Type of Material: Schedule & -0.330\\
Type of Material: Review & -0.324\\
Type of Material: Letter & -0.311\\
Section: Fashion \& Style & 0.275\\
Section: Movies & -0.267\\
Desk: National & 0.245\\
Section: Opinion & 0.245\\
Time of Day: 12-17 & 0.239\\
Section: Books & 0.219\\
Section: Health & 0.200\\
Section: Sports & -0.191\\
Desk: Society & -0.178\\
Section: Corrections & -0.167\\
Desk: BookReview & -0.167\\
\end{tabular}
\end{center}

@@

\begin{table}[hbt]
\caption{Comparison of MSEs for different model specifications}
\centering
\begin{tabular}{ccc}
\toprule
NN Trigram & Bigram & No Text\\
\midrule
2.392 & 2.389 &  2.502 \\
\bottomrule
\end{tabular}
\end{table}

>>>>

\begin{figure*}[ht]\centering
\includegraphics[width=\linewidth]{feature_weights_contd.png}
\caption{Linear Regression Feature Weights (excluding intercept term)}
\label{fig:lin_reg_weights}
\end{figure*}

@@

\begin{center}
\begin{tabular}{lr}
\toprule
Feature  &  Weight\\
\midrule
intercept & 8.964\\
log(Word Count) & 0.741\\
Desk: Foreign & 0.550\\
Desk: Travel & -0.465\\
Section: World & -0.402\\
Section: Opinion & 0.283\\
Type: BlogPost & -0.282\\
Type of Material: Schedule & -0.267\\
Desk: None & -0.262\\
Section: Movies & -0.239\\
Time of Day: 12-17 & 0.232\\
Type of Material: Review & -0.218\\
Desk: National & 0.211\\
Section: Health & 0.210\\
Section: Books & 0.201\\
Type of Material: Letter & -0.200\\
Type of Material: News & 0.187\\
Section: Sports & -0.175\\
Type of Material: Op-Ed & 0.170\\
Desk: BookReview & -0.154\\
\end{tabular}
\end{center}

@@

\begin{table}[hbt]
\caption{Comparison of MSEs for different model specifications}
\centering
\begin{tabular}{cccc}
\toprule
  & NN Trigram & Bigram & No Text\\
\midrule
Best Val. MSE & 2.392 & 2.389 &  2.502 \\
Train. MSE & 2.011 & 2.011 &  2.274 \\
OLS Val. MSE & 2.407 & 2.405 & 2.506 \\ 
\bottomrule
\end{tabular}
\end{table}
